Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-07-18 manuscript/manuscript.tex
notation suggestions for expectation in bootstrap world

Continuing using the notation in the independent case,
we use $F^{(b)}_n$ and $\hat\theta^{(b)}_n$ for the empirical distribution and
the estimated parameters based on the $b$th bootstrap sample,
$b = 1, \ldots, B$.
We then use block bootstrap to approximate the asymptotic distribution of
the KS statistic under $H_0$. Let $\hat{\theta}_0 = 
\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$. In particular, we
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)])$
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x; \theta_0))$, and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat{\theta}_0))$ as
an approximation of the distribution of 
$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$.
Here $\mathbb{E}^{(b)}$ denotes the expectation with respect to the bootstrap 
distribution 
(i.e., the randomness due
to the resampling using block bootstrap) conditional on the observations 
$X_1, \dots, X_n$.
The expected values $\mathbb{E}^{(b)}[F^{(b)}_n(x)]$ and
$\hat{\theta}_0 = \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
$\mathbb{E}^{(b)}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
$\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.

>>>>

As in the independent case,
we use $F^{(b)}_n$ and $\hat\theta^{(b)}_n$ for the empirical distribution and
the estimated parameters based on the $b$th bootstrap sample,
$b = 1, \ldots, B$.
We then use block bootstrap to approximate the asymptotic distribution of
the KS statistic under $H_0$. Let
$\hat{\theta}_0 = \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$, where
$\mathbb{E}^{(b)}$ denotes the expectation with respect to the
\jy{The superscript $(b)$ is unclear to me: we already used $b$ to
  index $1,  \ldots, B$. Can we use a star for this superscript?}
bootstrap distribution (i.e., the randomness due
to the resampling using block bootstrap) conditional on the observations 
$X_1, \dots, X_n$.
\jy{Specifically, how about using
  $\mathbb{E}^*$ denote the expectation in the bootstrap world?
  Then we can use
  $\mathbb{E}^*_B (F^{(b)}_n (x))= \frac{1}{B} \sum_{b = 1}^B
  F^{(b)}_n(x)$ to denote an approximator
  of $\mathbb{E}^* (F^{(b)}_n (x))$, and use
  $\mathbb{E}^*_B(\hat\theta_n^{(b)}) =
  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$ to
  denote an approximator of  
  $\hat{\theta}_0 = \mathbb{E}^*[\hat\theta^{(b)}_n]$?
}
In particular, we
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)])$
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x; \theta_0))$, and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_0))$ as
an approximation of the distribution of 
$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$.
Here 
The expected values $\mathbb{E}^{(b)}[F^{(b)}_n(x)]$ and
$\hat{\theta}_0 = \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$ can be
approximated by, respectively,
$\mathbb{E}^{(b)}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^B F^{(b)}_n(x)$ and
$\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
